SeedLing: Building and using a seed corpus \\ for the Human Language Project

### 2014-04-28 docs/computEL-final/data.tex
Edit data section.

Analysed texts, in addition to the raw text, contain more detailed annotations including parts of speech, morphological information, and syntactic relations.  This is stored as a table, where each row represents a word, and each column a type of information.  They propose the following columns: document ID, language code, sentence ID, word ID, wordform, lemma, morphological information, part of speech, gloss, head/governor, and relation/role.

>>>>

Analysed texts, in addition to the raw text, contain more detailed annotations including parts of speech, morphological information, and syntactic relations.  This is stored as a table, where each row represents a word, and columns can represent the following types of information: document ID, language code, sentence ID, word ID, wordform, lemma, morphological information, part of speech, gloss, head/governor, and relation/role.
